---
title: "Lab_7_Kermit"
author: "Eamon Devlin"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a comandment from the creator: From now on, all "commits" from this document shall be called "kermits" -the creator

But are they green????? -You dare defy the creator!!!!!!!! Blasphlamy!

If you are the collaborator:
-load the tidyverse
-read the kermit data as 'kermit'
-make some side-by-side histograms of the Score.pre for all respondents, separated by the Gender column

```{r}

library(tidyverse)
kermit <- read_csv("kermit.csv")

kermit_hist <- ggplot(kermit, aes(x = Score.pre)) +
  geom_histogram(bins = 4) +
  facet_wrap(~Gender)

kermit_hist

```

Perform rank based comparisions using the Mann-Whitney U and Wilcoxon-signed rank

Question: Is there a significant difference in pre-talk ranks of Kermit for male and female respondents

```{r}

mwu_kermit <- kermit %>% 
  wilcox.test(Score.pre ~ Gender, data = .)

mwu_kermit

# Null hypothesis: There is not a significant difference in ranks for male and female respondents

# Alternative: there is a significant difference in ranks

```

There was no significant difference in ranks for male and female respondents (W =155.5, p = 0.4, alpha = 0.05)


